Curriculum Vitae \\ \LARGE Maha Mohammed Nabeel El Meseery

### 2012-02-14 MyCv/Resyne.tex
adding the cv after the last paper is sumbitted

\setlength\topmargin{0in}
\setlength\headheight{0in}
\setlength\headsep{-0.25in}
\setlength\textheight{9.5in}
\setlength\textwidth{6.5in}
\setlength\oddsidemargin{-0.25in}
\setlength\evensidemargin{-0.25in}
\setlength\parindent{0in}
\setlength\parskip{0in}

\title {Curriculum Vitae \\ Maha Mohammed Nabeel El
Meseery\\ \small \textbf{ Address:} $2^{nd}$ Tahreer street, Dokki, Giza 12615,
Egypt. \\ \textbf{Tel:} (+2012)112- 5435, (+202)3336-8292.
\textbf{Email:} melmeseery@aucegypt.edu}
\date{}
\begin{document}

%%% remove comment delimiter ('%') and select language if required
%\selectlanguage{spanish}
\maketitle

 \section*{Education:}
  \begin{description}
\item [2004-2009]  \textbf{ Msc.E., Cairo University, Computer Engineering Department, Giza, Egypt}
  \begin{itemize}
    \item \textit{ Thesis Title:}\textbf{Sketch Recognition And Understanding}.
    \item \textit{Thesis Supervisors:} Prof. Nevin Darwish, Dr Magda Fayek , Prof. Samia
 Mashali , Mahmoud Fakr El Din
 \item \textit{ Graduate Courses:} Graduate Courses: Advanced Neural Networks, Image
 Processing and Computer Vision, Advanced Computer Networks, Advanced Database Systems, Embedded Systems, VLSI Testing, Numerical Analysis, and Technical Writing.

@@

 \begin{enumerate}
   \item Conducting and helping develop research in Online Arabic Handwriting
   Recognition. This includes implementing various features extraction and classification methods.
   \item Assisting in collecting, gathering and analyzing Online Arabic
   handwriting Datasets.
%   \item Assisting and developed research in area of Arabic and Latin digit
 %  Recognition.
 \item Implementing different features extraction and classification methods for Arabic and Latin digits and comparing their performance.
 \item Reading, analyzing and reviewing scientific and research papers.
 \item Guiding students in their studies in Lab projects and programming
 assignments.
 \item Conducting tutorials and problem sessions for students in various
 subjects.
\end{enumerate}

 \textbf{January 2007- present}\\
 \textbf{Research Assistant}, Electrical Research Institute, Egypt.
 \begin{enumerate}
\item Working as a member of the Signal Processing Lab in the Computer and
Systems Department.
 \item Assisting in the research project undergoing in the department.
 \item Implementing and developing different algorithms in field of Image
 Processing.
 \item Providing a technical support for other researchers especially in field
 of JavaEE programming.
\end{enumerate}

 \textbf{September 2005- September 2008 [part time from January 2007] }\\
 \textbf{Senior Software Engineer}, EngNet, Egypt.

@@

\item Introduced new software procedures in the company to enhance developers'
performance and collaboration.
 \item Analyzed and designed various software projects using UML and software engineering concepts.
 \item Wrote the software requirements and specifications of software
 application.
 \item Supervised and managed the development process for the developers and
 quality engineering teams.
 \item Assisted junior programmers in development using Java, JSP, Struts, RCP and MySQL.
\end{enumerate}

@@

 \section*{Publications:}
 \begin{enumerate}
  \item Online Library of Scientific Models - A New Way to Teach, Learn, and
Share Learning Experience, Elrefaei Hatem, Aboelfadel Tamer, Elmeseery Maha,
Elmofty Ali, Shafee Marwa, in Proceedings of the International Conference of "Interactive computer aided learning" ICL2007, Villach, Austria.\textbf{\underbar{}}
  \item El Meseery, Maha, Fakhr El Din, Mahmoud., Mashali, Samia., Fayek, Magda.
 \& Darwish, Nevin., Sketch Recognition Using Particle Swarm Algorithms,  IEEE
 International Conference on Image Processing, November,  2009, Cairo, Egypt.
  \item El Meseery, Sketch Recognition and Understanding,  Master Thesis,
  Faculty of Engineering, Computer Engineering Department, Cairo
  University, November, 2009, Egypt.
  \item El Meseery, Maha, Fakhr El Din, Mahmoud, Tarek abouldahab, Sketch
  Recognition using Enhanced Particle Swarm Optimization, Submitted to Pattern
  Recognition Letters, (17 pages Submitted in Dec 2010).
\end{enumerate}
 \section*{Awards:}
  \begin{enumerate}
    \item Jul 2003: Cairo University Award for Academic Distinction, Egypt.
	\item 1999 - 2003: Fellowship, Faculty of Engineering, Cairo University, Giza,
	Egypt.
  \end{enumerate}
 \section*{Computer Skills:}
 \begin{enumerate}
\item Environments: Linux (openSuse) and Windows.
 \item Programming: Java, JSP, Sturts, AJAX, .Net,C/C++, C\#,  ASP.NET, ASP, ADO.Net, ADO, VC6,  XML  Visual Basic, Embedded C, Assembly, Pascal, VHDL, Prolog, Lisp, Matlab, latex.
 \item Database Tools: SQL server 2000, MySql, Oracle and developer 6i.
 \item Analysis and Modeling: UML, Hardware design.
\end{enumerate}

 \section*{Training Courses and Summer jobs:}
 \begin{enumerate}
\item Human Development, Zedny Training Center, Cairo, Egypt (January - March 2005).
 \item MS SQL 2000, MSA University, Giza, Egypt (July 2004).
 \item C\# dot Net and ADO dot Net, MSA University, Giza, Egypt (August 2004).
 \item Web Development (ASP, XML, DOM, DHTML and ADO), Harf Information Technology. Cairo, Egypt (July --September 2002).
 \item DB2, JSP, Java beans, Servelts and IBM Web Sphere, Cairo University, Giza, Egypt (July- August 2001).
 \item Java applets, Training to develop an e-version of the calculus book
 taught to engineering students (August -- September 2000).
 \item MFC and VC6, Cairo University, Giza, Egypt (July 2000).
\end{enumerate}

@@

 \section*{Social Activities and Professional memberships:}

@@

\item[ \textbf{Dr. Mahmoud Fakhr El Deen}] (Researcher)

>>>>

\setlength\topmargin{0in}
\setlength\headheight{0in}
\setlength\headsep{-0.25in}
\setlength\textheight{9.5in}
\setlength\textwidth{6.5in}
\setlength\oddsidemargin{-0.25in}
\setlength\evensidemargin{-0.25in}
\setlength\parindent{0in}
\setlength\parskip{0in}
\title {Curriculum Vitae \\ \LARGE Maha Mohammed Nabeel El Meseery }
\date{\textbf{ Address:} $2^{nd}$ Tahreer street, Dokki, Giza 12615,
Egypt. \\ \textbf{Tel:} (+20122)112- 5435, (+202)3336-8292.
\textbf{Email:} melmeseery@aucegypt.edu}
\begin{document}
%%% remove comment delimiter ('%') and select language if required
%\selectlanguage{spanish}
\maketitle

% \begin{center}
% \line(1,0){450}\\
% \end{center}
\hline 
\hline 
 \section*{Education:}
  \begin{description}
\item [2004-2009]  \textbf{Msc.E., Cairo University, Computer Engineering Department, Giza, Egypt}
  \begin{itemize}
    \item \textit{ Thesis Title:}\textbf{Sketch Recognition And Understanding}.
    \item \textit{Thesis Supervisors:} Prof. Nevin Darwish, Dr Magda Fayek , Prof. Samia
 Mashali , Mahmoud Fakr El Din.
  \item \textit{ Graduate Courses:} Graduate Courses: Advanced Neural Networks, Image
  Processing and Computer Vision, Advanced Computer Networks, Advanced Database Systems, Embedded Systems, VLSI Testing, Numerical Analysis, and Technical Writing.

@@

 \begin{enumerate}
   \item Conducting and helping develop research on On-line Arabic Handwriting
   Recognition.  Including Conducting research on
    \begin{enumerate}
      \item On-line and offline information to solve isolated and cursive Arabic handwriting.
      \item Various features extraction methods.
      \item Various classification and pattern recognition methods.
   \end{enumerate}
   \item Assisting in collecting, gathering and analyzing On-line Arabic handwriting Datasets.
%   \item Assisting and developed research in area of Arabic and Latin digit
 %  Recognition.
 \item Conducted and helped with the research on Arabic and Latin handwritten digits by implementing different features extraction and classification methods to compare their performance.
 \item Reading, analyzing and reviewing scientific and research papers.
 \item Guiding students in their studies in Lab projects and programming
 assignments.
 \item Conducting tutorials and problem sessions for students in various
 subjects.
\end{enumerate}

 \textbf{January 2007- present}\\
 \textbf{Research Assistant}, Electrical Research Institute, Egypt.
 \begin{enumerate}
\item Working as a member of the Signal Processing Lab in the Computer and
Systems Department.
\item Conducting and helping develop research in various image processing. Including conducting research on
\begin{enumerate}
  \item Sketch recognition and hand drawn graphics.
  \item Using Swarm and Genetic optimization methods in Image processing.
  \item Face detection and recognition.
\item Landmine detection from GPR Images.
  \end{enumerate}
 \item Assisting in the research project undergoing in the department.

 \item Providing a technical support for other researchers especially in field
 of JavaEE programming.
 \item Design and develop the new ERI website.
\end{enumerate}

 \textbf{September 2005- September 2009 [part time from January 2007] }\\
 \textbf{Senior Software Engineer}, EngNet, Egypt.

@@

\item Introduced new software procedures in the company to enhance developers' performance and collaboration.
 \item Supervised and managed the development process for the developers and software quality teams.
 \item Assisted junior programmers in development using Java, JSP, Struts, RCP, Plug-in development and MySQL.
  \item Analyzed and designed various software projects using UML and software engineering concepts.
 \item Designed and developed various web applications in various commercial sectors.
 \item Wrote the software requirements and specifications of software application.
 \item Assisted in writing various grant/project proposals.
\end{enumerate}

@@

 \section*{Publications:}
 \begin{enumerate}
  \item Online Library of Scientific Models - A New Way to Teach, Learn, and Share Learning Experience, Elrefaei Hatem, Aboelfadel Tamer, Elmeseery Maha, Elmofty Ali, Shafee Marwa, in Proceedings of the International Conference of "Interactive computer aided learning" ICL2007, Villach, Austria.\textbf{\underbar{}}
  \item El Meseery, Maha, Fakhr El Din, Mahmoud., Mashali, Samia., Fayek, Magda \& Darwish, Nevin., Sketch Recognition Using Particle Swarm Algorithms,  IEEE International Conference on Image Processing, November,  2009, Cairo, Egypt.
  \item El Meseery, Sketch Recognition and Understanding,  Master Thesis, Faculty of Engineering, Computer Engineering Department, Cairo University, November, 2009, Egypt.
  \item El Meseery, Maha, Fakhr El Din, Mahmoud, Tarek abouldahab, Sketch Recognition using Enhanced Particle Swarm Optimization, Artificial Intelligence and Machine Learning (AIML), April 2011, vol 11 no. 1, p.1--7, 2011.
\item El Meseery, Maha, Fakhr El Din, Mahmoud,  El Nemer, Heba,  A Hybird Particle Swarm/Nelder-Mead Clustering Algorithm for Face Recognition, CiiT International Journal of Artificial Intelligent Systems and Machine Learning, Vol 3, No 10, September 2011. 
\item AbdelAzeem, Sherif, El Meseery, Maha, Arabic Handwriting Recognition using Concavity Features and Classifier Fusion, The tenth International Conference on Machine Learning and Applications (ICMLA'11),  Honolulu Hawaii USA, December 18-21, 2011. 
  \item AbdelAzeem, Sherif, El Meseery, Maha, Ahmed, Hany, On-line Arabic Handwritten Digits Recognition,(6 pages Submitted February 2012 to XIII International Conference on Frontiers in Handwriting Recognition, ).
\item El Meseery, Maha, Fakhr El Din, Mahmoud, Image based Landmine Detection,(10 pages submitted  February 2012 to Ain Shams Engineering Journal).
\end{enumerate}
 \section*{Awards:}
  \begin{enumerate}
    \item Jul 2003: Cairo University Award for Academic Distinction, Egypt.
	\item 1999 - 2003: Fellowship, Faculty of Engineering, Cairo University, Giza,
	Egypt.
  \end{enumerate}
 \section*{Computer Skills:}
 \begin{enumerate}
\item Environments: Linux (openSuse) and Windows.
\item Programming: Java, JSP, Sturts, AJAX, .Net,C/C++, Matlab, C\#,  ASP.NET, ASP, ADO.Net, ADO, VC6,  XML,  Visual Basic, Embedded C, Assembly, Pascal, VHDL, Prolog, Lisp,  latex.
 \item Frameworks: JavaSE, JavaEE, JavaME, Eclipse RCP, Eclipse Plugin development and Drupal.
 \item Database Tools: SQL server 2000, MySql, Oracle and developer 6i.
 \item Analysis and Modeling: UML, Hardware design.
\end{enumerate}

 \section*{Training Courses and Summer Jobs:}
 \begin{enumerate}
\item Human Development, Zedny Training Center, Cairo, Egypt (January - March 2005).
 \item MS SQL 2000, MSA University, Giza, Egypt (July 2004).
 \item C\# dot Net and ADO dot Net, MSA University, Giza, Egypt (August 2004).
 \item Web Development (ASP, XML, DOM, DHTML and ADO), Harf Information Technology. Cairo, Egypt (July --September 2002).
 \item DB2, JSP, Java beans, Servelts and IBM Web Sphere, Cairo University, Giza, Egypt (July- August 2001).
 \item Java applets, Training to develop an e-version of the calculus book
 taught to engineering students (August -- September 2000).
 \item MFC and VC6, Cairo University, Giza, Egypt (July 2000).
\end{enumerate}

@@

 \section*{Social Activities and Professional Memberships:}

@@

\item[ \textbf{Dr. Mahmoud Fakhr El Deen}] (Associate Professor)
